Typed Clojure: A Practical Optional Type System for Clojure

### 2012-09-11 dissertation/design-choices.tex
more grammar stuff

$$
\begin{tdisplay}{Test1}
\begin{altgrammar}
  \s{},\t{} &::= & \int \alt \bool \alt {\proctype {\s{}} {\t{}}} 
  &\mbox{Types}\\
  \M{}, \N{}, \P{}, \dots &::=& \x{} \alt \abs{\x{}}{\M{}} \alt
  \comb{\M1}{\M2}  &\mbox{Raw Terms} \\
\end{altgrammar}
\end{tdisplay} 
$$

$$
\begin{tdisplay}{Syntax of Terms}
\begin{altgrammar}
  \exp{} &::=&  \x{} \alt \{ \overrightarrow{\exp{}\ \exp{}} \} 
             \alt [ \overrightarrow{\exp{}} ] 
             &\mbox{Expressions} \\ 
  \v{} &::=& \alt \{ \overrightarrow{\v{}\ \v{}} \} 
             \alt [ \overrightarrow{\v{}} ] 
  &\mbox{Values} \\ 
\end{altgrammar}
\end{tdisplay}
$$

$$
\begin{tdisplay}{Operational Semantics}
\begin{array}{c}
{\inferrule[E-Assoc]
  { {\Gamma \vdash e_1 \hookrightarrow v_1} \\
    {\Gamma \vdash e_2 \hookrightarrow v_2} \\
    {\Gamma \vdash e_3 \hookrightarrow v_3} \\
    {v_4 = v_1\ with\ entry\ v_2\ to\ v_3} }
  { {\Gamma \vdash (assoc\ e_1\ e_2\ e_3) \hookrightarrow v_4} }} \\
\\
{\inferrule[E-Dissoc]
  { {\Gamma \vdash e_1 \hookrightarrow v_1} \\
    {\Gamma \vdash e_2 \hookrightarrow v_2} \\
    {v_3 = v_1\ without\ entry\ with\ key\ v_2}}
 {\Gamma \vdash (dissoc\ e_1\ e_2) \hookrightarrow v_3} } \\
\\
{\inferrule[E-Var]
  {\Gamma(x) = v}
  {\Gamma \vdash x \hookrightarrow v}}
\end{array} 
\end{tdisplay} 
$$

>>>>

%$$
%\begin{tdisplay}{Test1}
%\begin{altgrammar}
%  \s{},\t{} &::= & \int \alt \bool \alt {\proctype {\s{}} {\t{}}} 
%  &\mbox{Types}\\
%  \M{}, \N{}, \P{}, \dots &::=& \x{} \alt \abs{\x{}}{\M{}} \alt
%  \comb{\M1}{\M2}  &\mbox{Raw Terms} \\
%\end{altgrammar}
%\end{tdisplay} 
%$$

$$
\begin{tdisplay}{Syntax of Terms}
\begin{altgrammar}
  \exp{} &::=& (\exp{} \overrightarrow{\exp{}})         % function application, multiple arguments
             \alt \{ \overrightarrow{\exp{}\ \exp{}} \} % map literal
             &\mbox{Expressions} \\ 
   \v{} &::=& \k{} \alt \nil{}
               \alt \{ \overrightarrow{\v{}\ \v{}} \}   % map literal
              &\mbox{Values}
\end{altgrammar}
\end{tdisplay}
$$

$$
\begin{tdisplay}{Evaluation Contexts}
  \begin{altgrammar}
    \E{} &::=& % application rules
              (\E{}\ \overrightarrow{\exp{}})  % target first
              \alt (\v{}\ \overrightarrow{\v{}}\ \E{}\ \overrightarrow{\exp{}}) % arguments next
              % map rules
              \alt \{\overrightarrow{\v{}\ \v{}}\ \E{}\ \exp{}\ \overrightarrow{\exp{}\ \exp{}} \} % key first
              \alt \{\overrightarrow{\v{}\ \v{}}\ \v{}\ \E{}\ \overrightarrow{\exp{}\ \exp{}} \}   % value next
              % vector rule
              \alt [ \overrightarrow{\v{}}\ \E{}\ \overrightarrow{\exp{}} ] &\mbox{Evaluation Contexts}
  \end{altgrammar}
\end{tdisplay}
$$

$$
\begin{tdisplay}{Operational Semantics}
\begin{array}{c}
{\inferrule[E-Assoc]
  { {v_1 = \{ \overrightarrow{\v{}\ \v{}} \} } \\
    {v_4 = v_1\ with\ entry\ v_2\ to\ v_3} }
  { {\Gamma \vdash (assoc\ v_1\ v_2\ v_3) \hookrightarrow v_4} }} \\
\\
{\inferrule[E-Dissoc]
  { {v_1 = \{ \overrightarrow{\v{}\ \v{}} \} } \\
    {v_3 = v_1\ without\ entry\ indexed\ by\ v_2} }
  {\Gamma \vdash (dissoc\ v_1\ v_2) \hookrightarrow v_3} } \\
\\
{\inferrule[E-GetMapExist]
  { {v_1 = \{ \overrightarrow{\v{}\ \v{}} \} } \\
    {v_1\ has\ entry\ with\ key\ v_2} \\
    {v_3 = corresponding\ value\ in\ entry\ with\ key\ v_2\ in\ v_1} }
  { {\Gamma \vdash (get\ v_1\ v_2) \hookrightarrow v_3} }} \\
\\
{\inferrule[E-GetMapNotExist]
  { {v_1 = \{ \overrightarrow{\v{}\ \v{}} \} } \\
    {v_1\ has\ no\ entry\ with\ key\ v_2} \\
    {v_3 = \nil{}} }
  { {\Gamma \vdash (get\ v_1\ v_2) \hookrightarrow v_3} }}
\end{array} 
\end{tdisplay} 
$$

$$
\begin{tdisplay}{Type Syntax}
\begin{altgrammar}
  \T{} &::=& \Top \alt \Nil \alt \k{}
\end{altgrammar}
\end{tdisplay}{Type Syntax}
$$
